%-----------MEMBERSHIPS-----------------

\section{MEMBERSHIPS}

    \resumeSubheading
      {Sports}{Oxford, UK}
      {}{Oct. 2018 - present}
      \resumeItemListStart
        \resumeItem{\href{http://www.oxfordvolleyball.co.uk}{Oxford Volleyball Club} Oxford Falcons member playing in the \href{https://berkshirevolleyball.co.uk/calendar/2023-2024-ladies-division-1/}{BVA league}}{I love playing volleyball (as well as other racquet sports like tennis, squash and table tennis)!}

        \resumeItem{\href{https://ouvc.notion.site/ouvc/OUVC-Homepage-1d969e57c26c4426afc33d509b8736ca}{Oxford University Volleyball Club} Social media officer (Oct. 2019 - Dec. 2019) \& Women's 2nd team member}{I trained with the University team before the pandemic and briefly towards the end of 2022.}
     \resumeItemListEnd

    \resumeSubheading
      {\href{https://oxfordphilippinessociety.web.ox.ac.uk/home}{Oxford Philippines Society}}{Oxford, UK}
      {}{Oct. 2018 - present}
      \resumeItemListStart
        \resumeItem{Treasurer (Oct. 2018 - Sep. 2021) \& member}{Aside from managing finances and memberships, I organised monthly talks and social events as well.}
     \resumeItemListEnd
      
  \resumeSubheading
      {\href{https://psysc.org/}{Philippine Society of Youth Science Clubs, Inc.}}{Manila, PH}
      {}{Oct. 2012 - Jun. 2015}
      \resumeItemListStart
        \resumeItem{Events organiser \& member}{PSYSC promotes the public understanding of science, technology and the environment. I worked in as well as spearheaded committees organising national science camps, events and competitions attended by thousands of secondary school students.}
     \resumeItemListEnd

     %\resumeSubheading
     % {\href{https://en-gb.facebook.com/AngKlubTala/}{Klub Tala}}{Manila, PH}
     % {}{Oct. 2012 - Jun. 2015}
     % \resumeItemListStart
     %   \resumeItem{Vice president for Catechism (2013 - 2014) \& Member}{Klub Tala promotes the holistic development of Filipino children. As VP, I prepared content and materials for our weekly visits to an underprivileged community near our University and gave academic tutorials, catechism and values classes, and workshops (e.g. fashion, art) mixed in with fun activities and games to children.}

     %\resumeItemListEnd

%-----------OTHERS-----------------
%\section{OTHERS}
%  \resumeSubHeadingListStart
%    \resumeSubItem{Ed Padlan Awardee, 2nd place}{Sep. 2014, Manila PH; Given to the Top 2 (out of 33) students in my 3rd year in University.}
%    \resumeSubItem{Champion, Philippine National Chemistry Olympiad}{Apr. 2010, Manila PH}
%  \resumeSubHeadingListEnd
  
%-------------------------------------------